The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-27 article/article.tex
analysis is it's own major section
state results more clearly using theorems

@@

The \emph{Greedy} scheme achieves a maximum load of 
\[
\frac{m}{n} + \Theta\left(\frac{\log \log n}{\log d} \right)
\]
for all $m$ w.h.p. \cite{ABKU99} \cite{BCSV06}.

@@

\subsection{Analysis}
\label{sec:analysis}

\subsubsection{Preliminaries}
\label{sec:preliminaries}
\todo{where to put this? required for  bound of always-go-left in intro}
We define $d$-ary Fibonacci numbers as follows. For $k \leq0$, $F_d(k) = 0$, $F_d(1) = 1$ and for $k \geq 1$,

>>>>

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{theorem}[lemma]{Theorem}

@@

\todo{specify deletions; fix intro text since we now do use deletions}

\todo{use theorem from V\"ocking?}

\begin{theorem}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{m}{n} + \Theta\left(\frac{\log \log n}{\log d} \right)
\]
w.h.p.~at any time $t$ \cite{ABKU99} \cite{BCSV06}.

\end{theorem}

@@

\begin{theorem}
If $n$ balls are placed into $n$ bins using the Always-go-left scheme, the number of balls in the fullest bin will be 
\[
\frac{\ln\ln n}{d \ln \Phi_d} \pm \Theta(1)
\]
w.h.p.
\end{theorem}

\begin{theorem}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{\ln\ln n}{d \ln \Phi_d} + O(h)
\]
w.h.p.
\end{theorem}

\section{Analysis}
\label{sec:analysis}

\subsection{Preliminaries}
\label{sec:preliminaries}
\todo{where to put this? required for  bound of always-go-left in intro}
We define $d$-ary Fibonacci numbers as follows. For $k \leq0$, $F_d(k) = 0$, $F_d(1) = 1$ and for $k \geq 1$,
